---
title: "subpage.Rmd"
author: "ma"
date: "25/12/2022"
output: html_document
---

`r paste0('# ', Offence_group, '{data-navmenu="Select offence groups"}')`

`r shiny::tags$h1(Offence_group, align = "center", style="font-size:18px, font-thickness: 800%, color: #404040, font-weight: bold")`


```{r, include=FALSE}

#font-family: Courier; font-size:16px; font-weight:bold

# A SpatialPointsDataFrame for the map.
# Set a group name to share data points with the table.
brew_sp <- SharedData$new(subpage_data, group = "idd")

# A regular data frame (without coordinates) for the table.
# Use the same group name as the map data.
brew_data <- as_tibble(subpage_data) %>%
  dplyr::select(brewery, address, village, founded) %>%
  data.frame()
  #SharedData$new(group = "id") #to do the joining

#head(brew_data)

map <- leaflet(brew_sp) %>%
  addTiles() %>%
  addMarkers()

##map

#
tbl <- reactable(
  brew_data[1:32,] %>%
    dplyr::mutate(Name = substr(village, 1, 5)) %>%
    dplyr::mutate(founded2 = founded-1800)%>%
    dplyr::filter(!is.na(founded2))%>%
    dplyr::select(Name, founded2)%>%
    dplyr::mutate(founded2 = as.numeric(if_else(Name == "Adels", paste("0"), paste(founded2)))) %>%
    tibble::rownames_to_column("Sn")%>%
    dplyr::mutate(Sn=paste("#", Sn, sep="")),
  #selection = "multiple",
  onClick = "select",
  # borderless = TRUE,
  # highlight = TRUE,
  # rowStyle = list(cursor = "pointer"),
  #defaultSelected = c(1:10),
  #defaultPageSize = 20,
  columns = list(
  founded2 = colDef(
      cell = function(value) {
       if (value > 0) {
        img_src <- image_uri(paste(getwd(), "img/up_arrow.jpg", sep="/"))
        image <- img(src = img_src, style = "height: 25px;", alt = value)
        tagList(
        div(style = "display: inline-block; width: 25px", image),
        paste0("+", value, "%")
        )} else if (value < 0) {
        img_src <- image_uri(paste(getwd(), "img/down_arrow.jpg", sep="/"))
        image <- img(src = img_src, style = "height: 25px;", alt = value)
        tagList(
        div(style = "display: inline-block; width: 25px", image),
        paste0(value, "%")
    )} else
        # img_src <- image_uri(paste(getwd(), "img/dash.jpg", sep="/"))
        # image3 <- img(src = img_src, style = "height: 15px;", alt = value)
        # tagList(
        # div(style = "display: inline-block; width: 20px", image3),
        paste0(value, "%")
        #)
  },
    #align = "left",
      style = function(value) {
        color <- if (value > 0) {
          "#e00000"
        } else if (value < 0) {
          "#008000"
        } else "blue"
        list(fontWeight = 600, color = color)
      }
    )
  ),
 #rownames = TRUE,
  # pagination = FALSE,
  #searchable = TRUE,
 pageSizeOptions = c(15, 30),
 defaultPageSize = 15,
 showPagination = TRUE,
 fullWidth = TRUE,
 showSortable = TRUE,
  height = 600,
  wrap = FALSE,
  compact = FALSE,
  highlight = TRUE,
  bordered = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"),
    searchInputStyle = list(width = "100%")
    ),
  minRows = 8
)
#

tbl

```

Column {.sidebar data-width=200}
-----------------------------------

## Row 1 {data-height=80}

### **Trend and Change Points** {data-width=1200}

```{r, include=TRUE}
# mm1 <- htmltools::browsable(
#   htmltools::tagList(map, tbl)
#   #htmltools::tagAppendChild(tag1, tbl)
# )
# mm1

```


### **Summary**

```{r, include=TRUE}
#Create table that shows
#Overall trend
#Change points
```

## Row 2 {data-height=170}

### **Offence per 1,000 people (LSOA units)**{data-width=200}

```{r eval=FALSE}

#render map
map3 <- leaflet() %>%
  addTiles %>%
  addPolygons(data =   bckgrnd2, #
              color="white",
              #label = ~FILE_NAME,
              labelOptions = labelOptions(
                noHide = T, textOnly = T,
                textsize = 22,
                style = list('color' = "white")
              ),
              ##color = ~colorQuantile("gray", gm_la$FILE_NAME)(FILE_NAME),
              fillOpacity = 1,
              group = "background")%>%
 #addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(data = gm_la %>% filter(FILE_NAME == "ROCHDALE"), weight = 1,  #all la boundaries
              color="black",
              #label = ~FILE_NAME,
              labelOptions = labelOptions(
                noHide = T, textOnly = T,
                textsize = 22,
                style = list('color' = "black")
              ),
              ##color = ~colorQuantile("gray", gm_la$FILE_NAME)(FILE_NAME),
              fillOpacity = 0.1,
              group = "la")
  # addTiles %>%
  # setView(-2.271, 53.504, zoom = 1.5) %>% syncWith("maps")%>%
  # addPolygons(data =   gm_bdry, #
  #             color="white",
  #             #label = ~FILE_NAME,
  #             labelOptions = labelOptions(
  #               noHide = T, textOnly = T,
  #               textsize = 22,
  #               style = list('color' = "white")
  #             ),
  #             ##color = ~colorQuantile("gray", gm_la$FILE_NAME)(FILE_NAME),
  #             fillOpacity = 1,
  #             group = "background")#%>%

map3
```

```{r, include=TRUE}
mm2 <- htmltools::browsable(
  #attachDependencies(map,
  htmltools::tagList(map, tbl))
  #htmltools::tagAppendChild(tag1, tbl)
#)

mm2
```


### **Direction of Crime rates in Neighbourhoods (Sorted by most recent year)**

```{r, include=TRUE, fig.width=2, fig.height=2}

# mm3 <-  htmltools::tagList(tbl)
# mm3

mm3 <- htmltools::browsable(
  htmltools::tagList(tbl))

mm3


```

## Row 3 {data-height=30}

### Key map feature

### Further details



## Row 4 {data-height=100}

### **Age-Sex Profile**

### **Age-Ethnicity Profile**

### **Age-Occupation Profile**


## Row 5 {data-height=20}

### Description

### Description

### Description


<!-- ```{r, include=TRUE, fig.width=2, fig.height=2} -->

<!-- #https://stackoverflow.com/questions/55011733/modify-text-size-in-shiny -->

<!-- # mm3 <-  htmltools::tagList(tbl) -->
<!-- # mm3 -->

<!-- mm3 <- htmltools::browsable( -->
<!--   htmltools::tagList(tbl)) -->

<!-- mm3 -->


<!-- ``` -->

